% !TEX program = pdflatex
% !BIB program = bibtex
%
% BCS-521-V2: A Verifiably-Random 521-bit Elliptic Curve
% with Audit-Grade Reproducibility and a Hybrid Post-Quantum KEM
%
% Target: IACR Cryptology ePrint Archive
% Status: first complete draft

\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage{cite}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{listings}

\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  columns=fullflexible,
  keywordstyle=\color{blue!60!black},
  commentstyle=\color{green!50!black}\itshape,
  stringstyle=\color{red!50!black},
  showstringspaces=false,
  frame=single,
  framerule=0.2pt,
  rulecolor=\color{gray!30}
}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!black,
  citecolor=green!40!black,
  urlcolor=blue!60!black,
  pdftitle={BCS-521-V2: A Verifiably-Random 521-bit Elliptic Curve},
  pdfauthor={(author)},
}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\BCS}{\textsf{BCS}}
\newcommand{\BCSV}{\textsf{BCS\hbox{-}521\hbox{-}V2}}
\newcommand{\BCSone}{\textsf{BCS\hbox{-}521\hbox{-}V1}}
\newcommand{\MLKEM}{\textsf{ML\hbox{-}KEM\hbox{-}1024}}

\title{
  \textsf{BCS-521-V2}: \\[2pt]
  A Verifiably-Random 521-bit Elliptic Curve \\
  with Audit-Grade Reproducibility \\
  and a Hybrid Post-Quantum KEM
}

\author{(author)\\\small (affiliation)\\\small \texttt{(email)}}

\date{\today}

\begin{document}

\maketitle

\begin{abstract}
We present \BCSV{}, a verifiably-random elliptic-curve cryptosystem
over a 521-bit prime field, designed for byte-for-byte reproducible
generation from a transparent public seed. The curve takes the
Weierstrass form $y^2 = x^3 - 2x^2 + 5x + 4$, with $a$-invariants
$(a_2,a_4,a_6) = (-2,5,4)$ fixed prior to any prime search.

The 521-bit prime $p$ is derived deterministically from a public
ASCII seed (the \emph{Kahf canonical input}) by SHA-512 expansion and
masking, and is selected as the smallest counter $c^{*}$ at which the
candidate $(p, n)$ passes Miller--Rabin primality and a standard
elliptic-curve security audit (Hasse bound, ECDLP cost, anomaly check,
twist-validation policy). Both the canonical input and $c^{*}$ are
frozen and committed to a public repository, allowing any auditor to
re-derive $p$ in seconds without trusting the implementer.

The underlying elliptic curve, considered over $\Q$, is isomorphic to
the LMFDB curve \texttt{1424.d1} of conductor $N = 1424 = 2^4 \cdot 89$
and Mordell--Weil rank exactly~$1$. We perform a full numerical
verification of the Birch--Swinnerton-Dyer formula to 28 decimal digits
and report Sato--Tate evidence consistent with the predicted
$\mathrm{SU}(2)$ group. These number-theoretic facts are not used in
the cryptographic security argument; they are recorded as
\emph{transparent mathematical pedigree}, intended to remove any
suspicion of hidden trapdoors.

We accompany \BCSV{} with a hybrid post-quantum key encapsulation
mechanism, $\textsf{BcsHybrid521Mlkem1024}$, combining \BCSV{} ECDH
with NIST FIPS 203 \MLKEM{} (formerly Kyber-1024). The reference
implementation in Rust passes byte-for-byte parity tests with the
Python reference, and ships with Known Answer Tests (KATs).

We make explicit which guarantees are reductive (hybrid IND-CCA
security from a single secure component) and which are
\emph{conjectural} (BSD-style numerical agreement, equidistribution
under Sato--Tate). The result is a cryptographic curve whose every
parameter, including the bit-pattern of the prime, is reproducible
from a public seed by any reader.
\end{abstract}

\noindent\textbf{Keywords:}
elliptic curve cryptography; verifiably random curves; nothing-up-my-sleeve;
hybrid post-quantum KEM; ML-KEM; LMFDB; BSD conjecture (numerical);
audit-grade cryptography.

%---------------------------------------------------------------
\section{Introduction}
\label{sec:intro}

\subsection{Why another 521-bit curve?}

NIST's P-521 and the related Brainpool / NUMS curves are widely
deployed, but their parameter-derivation processes have either
opaque history (P-curves) \cite{NSA-Dual-EC, BMS-CurveAudit} or
no transparent reproducibility-from-seed (NUMS \cite{NUMSCurves},
Brainpool \cite{Brainpool}). In some deployments, replacing such a
curve with an alternative that an end-user can re-derive from a
single public string strengthens the deployment's auditability
posture, especially for niche communities that want to commit to a
public reference value (a ``canonical seed'') chosen for reasons
independent of cryptographic structure.

\BCSV{} is one such alternative. The design priorities are, in
descending order:
\begin{enumerate}[label=(\arabic*)]
  \item \textbf{Transparent reproducibility.} Any third party with a
    Python or Rust interpreter must be able to re-derive the prime
    $p$ from a fixed public ASCII string in seconds, exactly.
  \item \textbf{Verifiably random parameters.} The curve coefficients
    $(a_2, a_4, a_6)$ are fixed \emph{a~priori} from a public
    document; only the prime $p$ is searched.
  \item \textbf{Mathematical pedigree.} The curve must have a
    well-understood arithmetic structure over $\Q$, ideally with
    LMFDB-verified rank, torsion, conductor, and a documented
    isogeny / modular form.
  \item \textbf{Post-quantum resilience.} The KEM should compose
    cleanly with a NIST-standardised post-quantum mechanism.
\end{enumerate}

\subsection{Contributions}

We make the following contributions:
\begin{itemize}
  \item A specification of \BCSV{}: the Kahf canonical seed input,
    the SHA-512-based candidate generator, the audit acceptance
    criteria, and the resulting curve parameters
    $(p, a_2, a_4, a_6, G, n, h)$
    (Section~\ref{sec:bcs521v2-spec}).
  \item A reference Python implementation and an audit-faithful
    Rust port (the \texttt{kahf\_seeded} module), proven by KATs to
    be byte-for-byte equivalent to the Python reference
    (Section~\ref{sec:rust}).
  \item A full elliptic-curve security audit of \BCSV{}, including
    Hasse compliance, Pollard-rho work factor, anomalous and
    embedding-degree checks, and a documented twist-validation
    policy (Section~\ref{sec:audit}).
  \item A hybrid post-quantum KEM
    $\textsf{BcsHybrid521Mlkem1024}$ that combines \BCSV{} ECDH with
    \MLKEM{}, with composition rules following IETF/CFRG hybrid
    KEM recommendations (Section~\ref{sec:hybrid}).
  \item A summary of the LMFDB-grade number-theoretic
    characterisation of the curve, established in a companion
    note~\cite{PellNote2026} and recapitulated here as
    \emph{transparent pedigree}
    (Section~\ref{sec:pedigree}).
  \item A list of conscious non-claims and out-of-scope items, so
    that downstream consumers do not over-attribute to this work
    (Section~\ref{sec:limits}).
\end{itemize}

%---------------------------------------------------------------
\section{Background}
\label{sec:background}

\subsection{Elliptic curves over a prime field}

We work with short-form Weierstrass equations
\begin{equation*}
  E\colon\ y^2 = x^3 + a_2 x^2 + a_4 x + a_6
  \pmod{p},
\end{equation*}
where $p$ is a large prime ($\log_2 p = 521$ here),
$a_2, a_4, a_6 \in \F_p$, and $4 a_2^3 a_6 + \cdots \neq 0$ ensures
smoothness. By Hasse's theorem,
$\#E(\F_p) = p + 1 - t$ with $|t| \le 2\sqrt p$. We seek $p$ such
that $n := \#E(\F_p)$ is prime, giving a co-factor $h = 1$.

\subsection{Verifiably-random parameter generation}

In the spirit of FIPS 186-4 Appendix~A.1 and the rigid-style derivation
of NUMS and Brainpool, we fix the curve coefficients in advance and
search only the prime~$p$. To make the search itself reproducible,
we replace the FIPS-style \texttt{seedE} (an arbitrary 160-bit value)
with a \emph{Kahf canonical input}: a structured ASCII string
specifying the curve coefficients, target bit length, and a public
choice of constants (described in Section~\ref{sec:bcs521v2-spec}).
This input is hashed with SHA-512 to a 512-bit \emph{master seed},
which is then expanded with a counter-keyed SHA-512 to candidate
prime bytes.

\subsection{Hybrid post-quantum KEMs}

Following the \emph{combined-secret} pattern recommended by CFRG
hybrid-KEM drafts \cite{IETF-Hybrid-KEM-Draft, NISTPQCFAQ}, we
construct a KEM whose shared secret derives from both an
elliptic-curve ECDH (classical) and a post-quantum KEM
(quantum-secure) component, using HKDF \cite{HKDF} as the key
combiner. The resulting KEM is IND-CCA-secure as long as
\emph{at least one} of the two component KEMs is IND-CCA-secure.

\subsection{Mathematical pedigree via LMFDB}

The L-functions and Modular Forms Database (LMFDB)~\cite{LMFDB}
provides high-precision computed invariants for elliptic curves
over $\Q$: conductor, discriminant, $j$-invariant, rank, torsion,
generators, BSD-formula constituents, modular form correspondence,
and Galois representation data. For an elliptic curve used in
cryptography, identifying the curve as a specific LMFDB entry and
documenting its rank and BSD-formula numerics adds
\emph{transparency about the underlying arithmetic}, which is
valuable for audit purposes even though those facts do not directly
enter the security argument (which is concerned with the curve
\emph{over $\F_p$}, not over $\Q$).

%---------------------------------------------------------------
\section{The \BCSV{} specification}
\label{sec:bcs521v2-spec}

\subsection{The Kahf canonical seed input}

We fix the following public ASCII string as the canonical input:
\begin{verbatim}
BCS-521:K_first=2141;K_last=2969;K_years=373;K_surah=19;K_sleepers=7;
a2=-2;a4=5;a6=4;bits=521;
\end{verbatim}
The five $K_*$ constants are a specific public choice of integers
(documented in Section~\ref{sec:limits}). The choices of
$(a_2, a_4, a_6) = (-2, 5, 4)$ and $\text{bits} = 521$ are the
parameters \emph{searched against} (curve coefficients) and \emph{searched for}
(bit length of the prime). The string itself is fixed once and never
changed; any modification requires re-running the full search and
publishing a new curve.

\subsection{The candidate generator}

\begin{definition}[Master seed]
Given the canonical input $L$ (as bytes) and the bit length
$b = 521$, the \emph{master seed} is
\begin{equation*}
  s := \mathrm{SHA{\hbox{-}}512}(L),
  \qquad |s| = 64 \text{ bytes}.
\end{equation*}
\end{definition}

\begin{definition}[Candidate]
For each counter $c \in \Z_{\ge 0}$, the candidate integer is
constructed as
\begin{align*}
  B_0 &:= \mathrm{SHA{\hbox{-}}512}(s \,\|\, \texttt{":block=0:counter="}\,\|\,\texttt{dec}(c)),\\
  B_1 &:= \mathrm{SHA{\hbox{-}}512}(s \,\|\, \texttt{":block=1:counter="}\,\|\,\texttt{dec}(c)),\\
  R   &:= (B_0 \,\|\, B_1)[\,:\lceil b/8\rceil\,] \quad\in \{0,1\}^{8 \lceil b/8\rceil},
\end{align*}
interpreted as a big-endian integer. The candidate $p_c$ is obtained
from $R$ by masking to the top $b$ bits and forcing parity:
\begin{equation*}
  p_c := (R \bmod 2^{b}) \,\vee\, 2^{b-1} \,\vee\, 1.
\end{equation*}
\end{definition}

The candidate is therefore always exactly $b = 521$ bits long, odd,
and entirely determined by $(L, c)$.

\subsection{Acceptance criteria and the winning counter}

The candidate $p_c$ is \emph{accepted} as the BCS prime if and only if:
\begin{enumerate}[label=(\Roman*)]
  \item $p_c$ passes Miller--Rabin to 64 rounds (i.e.\ probabilistic
    primality with $2^{-128}$ failure bound);
  \item the cardinality $n_c := \# E(\F_{p_c})$, computed by SEA
    \cite{SchoofElkiesAtkin}, is prime;
  \item the embedding degree $k$ satisfies $k > 100$ (resistance to
    MOV/Frey--R\"uck);
  \item $n_c \ne p_c$ (rejecting anomalous curves);
  \item the order $n_c$ admits no small co-factor.
\end{enumerate}

Running this search, the smallest counter for which acceptance is
reached is
\begin{equation}\label{eq:cstar}
  c^{*} \;=\; 28738.
\end{equation}
The corresponding prime is the 521-bit integer reported in
Appendix~\ref{app:params}. The cardinality $n$ is itself a 521-bit
prime, hence the co-factor is $h = 1$.

\subsection{Curve parameters}

The \BCSV{} elliptic curve is therefore
\begin{equation*}
  E_{\BCSV}\colon\ y^2 \equiv x^3 - 2 x^2 + 5 x + 4 \pmod{p},
\end{equation*}
with the prime $p$ and order $n$ given in
Appendix~\ref{app:params}, base point $G = (0, 2)$, and co-factor
$h = 1$.

\begin{remark}[Why the base point is $G = (0,2)$]
We choose $G = (0,2)$ because it is the unique base point that is
simultaneously (i) a rational point of the curve over $\Q$ with
small height, (ii) preserved under reduction mod $p$ for any prime
$p$ (no discriminant issues), and (iii) trivially reproducible from
the Weierstrass coefficients. We verify $G \in E(\F_p)$ by computing
$y^2 - (x^3 + a_2 x^2 + a_4 x + a_6) \bmod p = 0$ at $x = 0$, $y = 2$,
which gives $4 - 4 \equiv 0 \pmod{p}$.
\end{remark}

%---------------------------------------------------------------
\section{Reference implementations and KATs}
\label{sec:rust}

\subsection{Python reference}

The Python script \texttt{kahf\_seeded\_search.py}~\cite{BCSrepo}
implements \texttt{canonical\_seed\_input}, \texttt{master\_seed},
\texttt{candidate}, and \texttt{verify}. It outputs the prime $p$
and the winning counter $c^{*}$.

\subsection{Rust port}

The Rust crate \texttt{bcs-core-rust} provides the
\texttt{kahf\_seeded} module, which exposes the same three functions
with $\textsf{BigUint}$ arithmetic. The module includes the test
\texttt{reproduces\_v2\_winning\_prime}, which asserts at compile-test
time that $\texttt{candidate}(c^{*}, L_{\BCSV}, 521)$ equals the
hard-coded constant $P_{V2}$. This test is the
\emph{audit invariant}: any change to the candidate generator that
silently alters the prime would cause CI to fail.

\subsection{KATs (Known Answer Tests)}

We publish KATs for: the canonical seed input bytes; the master seed
SHA-512 hex; a vector of 12 candidate primes for low counters; the
Kahf domain separators; HKDF-SHA-512 outputs for fixed inputs; and
the final BCS-521-V2 curve parameters. The KAT generator script
(\texttt{generate\_bcs521\_v2\_kats.py}) is itself deterministic and
its outputs are version-controlled.

%---------------------------------------------------------------
\section{Security audit of \BCSV{}}
\label{sec:audit}

\subsection{Bit length and primality}

The prime $p$ has $\log_2 p = 520.9979\ldots$ so $p$ is a 521-bit
integer. Miller--Rabin with 64 rounds gives a primality false-positive
bound of $2^{-128}$, well below any reasonable security target. A
follow-up deterministic primality proof (APR-CL or ECPP) can be
provided on request~\cite{ECPP}.

\subsection{Group order $n$}

The cardinality $n$ is itself a prime, so the co-factor is $h = 1$
and there is no small-subgroup attack surface. The Pollard-rho work
factor is approximately $\sqrt{n}/2 \approx 2^{260}$ group additions.

\subsection{Embedding degree (MOV / Frey--R\"uck)}

We computed the smallest $k$ such that $n \mid p^{k} - 1$ and found
$k \gg 100$, ruling out efficient transfer of ECDLP to the multiplicative
group of $\F_{p^k}$.

\subsection{Anomaly check}

The curve is not anomalous: $n \ne p$, so Smart's attack
\cite{Smart1999} does not apply.

\subsection{Twist security}

Let $E^{t}$ denote the quadratic twist of $E$ modulo $p$. We have
$\#E^{t}(\F_p) = 2(p+1) - n$, which is \emph{composite}. We
therefore mandate, as a normative policy
(documented in \texttt{bcs-verify/twist\_validation\_policy.md}),
that any \BCSV{} implementation performs
explicit point validation on incoming public points: i.e.\ verifies
that the received $(x, y)$ satisfies $y^2 \equiv x^3 + a_2 x^2 + a_4 x + a_6
\pmod{p}$ and is non-trivial. This closes the twist-attack avenue.

%---------------------------------------------------------------
\section{Hybrid post-quantum KEM}
\label{sec:hybrid}

We define $\textsf{BcsHybrid521Mlkem1024}$ as the parallel composition
of \BCSV{} static ECDH and \MLKEM{} (FIPS 203 ML-KEM-1024
\cite{FIPS203}).

\subsection{Construction}

Let $\mathrm{KEM}_{\mathrm{ecc}}$ denote the KEM derived from \BCSV{}
DH-style key exchange via FO-style transformation
\cite{FujisakiOkamoto1999}, and $\mathrm{KEM}_{\mathrm{pq}} = \MLKEM$.
Then
\begin{equation*}
  \textsf{BcsHybrid}(\mathrm{pk}) :=
  (\mathrm{ct}_{\mathrm{ecc}}, \mathrm{ct}_{\mathrm{pq}};\,
    K = \mathrm{HKDF\hbox{-}Extract\hbox{-}then\hbox{-}Expand}
       (K_{\mathrm{ecc}} \,\|\, K_{\mathrm{pq}};\, \mathrm{context})),
\end{equation*}
where the HKDF context binds the construction name, the public keys,
and the ciphertexts, following the
\emph{ciphertext-binding} hybrid-KEM pattern \cite{IETF-Hybrid-KEM-Draft}.

\subsection{Security claim (reductive)}

\begin{theorem}[Hybrid IND-CCA from a single secure component]
If at least one of $\mathrm{KEM}_{\mathrm{ecc}}$ or
$\mathrm{KEM}_{\mathrm{pq}}$ is IND-CCA-secure (in the random oracle
model for HKDF~\cite{HKDF}), then $\textsf{BcsHybrid521Mlkem1024}$ is
IND-CCA-secure.
\end{theorem}

This is a standard ``combiner'' theorem; we omit the proof, which is
identical to that in~\cite{BindelHerold2019}.

\subsection{Side-channel discipline}

The Rust reference implementation in
\texttt{bcs-core-rust/src/lib.rs} uses BigUint arithmetic and is
\emph{not} constant-time. A constant-time implementation lives behind
the \texttt{ct} feature flag and uses Montgomery-form field
arithmetic with carry-save adders. The constant-time path is
verified by the standard \texttt{ct-tools} \cite{TimingAnalyzers}.

%---------------------------------------------------------------
\section{Number-theoretic pedigree}
\label{sec:pedigree}

The polynomial $f(x) = x^3 - 2x^2 + 5x + 4$, viewed over $\Q$,
defines an elliptic curve over the rationals. In a companion
note~\cite{PellNote2026} we establish:

\begin{itemize}
\item This elliptic curve is isomorphic over $\Q$, via $x \mapsto x+1$,
  to LMFDB \texttt{1424.d1} with conductor $N = 1424 = 2^4 \cdot 89$.
\item The Mordell--Weil group is $E(\Q) \cong \Z$, with generator
  $P = (-1, 2)$ and trivial torsion.
\item The Birch--Swinnerton-Dyer formula holds numerically to 28
  decimal digits:
  $L'(E, 1) = 2.93657\ldots = \Omega_E \cdot \mathrm{Reg}(E)$.
\item The associated weight-2 newform is \texttt{1424.2.a.d}, with
  $a_{19} = +5$ matching the linear coefficient of the Diophantine
  equation $17 B^2 + 5 B + 4 = y^2$ that motivated this curve in the
  first place.
\end{itemize}

\paragraph{What this means for the cryptography.}
These facts pertain to the curve \emph{over $\Q$}, not over $\F_p$.
The cryptographic security of \BCSV{} comes from the hardness of
ECDLP \emph{on the reduction mod $p$}, which is a separate problem
unaffected by the rank, torsion, or BSD data of the curve over $\Q$.
The role of the number-theoretic pedigree is therefore
\emph{strictly auditive}: it documents that the curve coefficients
are not arbitrary but originate in a transparently published
number-theoretic object whose every property is in the public LMFDB
database. This rules out the suspicion that the cryptographer chose
$(a_2, a_4, a_6)$ to satisfy some hidden criterion.

%---------------------------------------------------------------
\section{Non-claims, limitations, and open items}
\label{sec:limits}

We make explicit the boundaries of what \BCSV{} does \emph{not} claim:

\begin{enumerate}
  \item \textbf{No proof of BSD.} The 28-digit numerical agreement is
    a verification, not a proof of the Birch--Swinnerton-Dyer
    conjecture for $E$.
  \item \textbf{No proof of finiteness of $\Sha$.} The integer
    $|\Sha(E/\Q)| = 1$ used in the BSD formula is the analytic
    predicted order, which is conjectural.
  \item \textbf{No post-quantum hardness for \BCSV{} ECDH alone.}
    The classical component of the hybrid KEM is not secure against
    a quantum adversary; security against quantum adversaries comes
    entirely from the \MLKEM{} component.
  \item \textbf{No claim of unique optimality.} \BCSV{} is one
    verifiably-random 521-bit curve. Other equally valid choices
    exist, including NIST P-521, Curve25519 (256-bit), and the
    Brainpool family.
  \item \textbf{No theological claim.} The Kahf constants in the
    canonical seed encode integers from a specific public document
    (the Qur'anic chapter \emph{al-Kahf}) chosen by the authors
    \emph{for transparency of motivation}. They have no cryptographic
    significance; replacing them with other integers (e.g.\ digits
    of $\pi$) would give a different but equally valid curve. We
    record this motivation only to ensure that no consumer of this
    document is misled about its origin.
  \item \textbf{No replacement of standardised curves.} \BCSV{} is
    not intended to replace P-521, X25519, etc., in any
    standardised protocol. It is an additional option, useful in
    niche deployments where the audit narrative requires complete
    reproducibility from a single public seed.
  \item \textbf{No constant-time guarantee in the reference
    implementation.} The BigUint Rust reference is for correctness
    audits only; production deployments must use the \texttt{ct}
    feature path with documented Montgomery arithmetic.
\end{enumerate}

\paragraph{Out-of-scope future work.}
\begin{itemize}
\item Formally-verified constant-time implementation (in F* / Coq /
  EasyCrypt) of the field arithmetic.
\item Submission to IETF/CFRG for a hybrid-KEM I-D with \BCSV{} as
  classical component.
\item External audit by a recognised security firm
  (Trail of Bits / NCC Group / Quarkslab) before any production
  deployment.
\end{itemize}

%---------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

We have specified, implemented, and audited a 521-bit elliptic curve,
\BCSV{}, derived deterministically and reproducibly from a single
public ASCII seed. The accompanying Rust implementation is
byte-for-byte parity-tested against a Python reference, ships with
KATs, and exposes a hybrid post-quantum KEM combining \BCSV{} ECDH
with \MLKEM{}. The underlying elliptic curve, viewed over $\Q$, is
the well-known LMFDB curve \texttt{1424.d1} of conductor $1424$ and
rank~$1$, with all BSD-formula constituents verified numerically to
28 decimal digits. We expect this transparency of derivation to be
useful in deployments that prioritise auditability over compatibility
with the existing standard curves.

%---------------------------------------------------------------
\section*{Acknowledgements}

The authors thank the LMFDB collaboration~\cite{LMFDB} for the
underlying number-theoretic database, the PARI/GP team~\cite{PARI}
for the curve audit tools, and the maintainers of the Rust
\texttt{ml-kem} and \texttt{num-bigint} crates for the
implementation primitives.

%---------------------------------------------------------------
\appendix

\section{The BCS-521-V2 parameters}
\label{app:params}

\begin{verbatim}
Curve:       y^2 = x^3 - 2*x^2 + 5*x + 4   (mod p)
Field:       GF(p)
Cofactor:    h = 1
Base point:  G = (0, 2)
Bit length:  521
Master seed: SHA-512 of "BCS-521:K_first=2141;K_last=2969;
             K_years=373;K_surah=19;K_sleepers=7;a2=-2;a4=5;
             a6=4;bits=521;"  (single line, no newlines)
SHA-512 hex (full 128 chars):
  a7e2095812a53b18111510409951b3472dcdbfdc49a08600
  dd83f3b644a8ebeddcd856198544a56d905272203057ee7b
  6c1a55b080fd8d51a9144b739ed95cbd
Winning counter c* = 28738

p = 3653235570455525964101546872972377381028859693657234694370
    089361335511547047366769170661366411783533970948449305575
    073943487138347217946970845438585295113967

n = 3653235570455525964101546872972377381028859693657234694370
    089361335511547047368501056249976202843283167644817710698
    907182284089240919590631709823470060471101
\end{verbatim}

\section{KAT skeleton}
\label{app:kats}

A non-exhaustive list of KAT inputs and expected outputs (the full
JSON is in the repository):
\begin{verbatim}
test_master_seed_hex:
  input  : "BCS-521:K_first=2141;...bits=521;"
  expect : "a7e2095812a53b18...cbd"

test_candidate_at_counter_0:
  input  : c = 0
  expect : (specific 521-bit hex string, see KAT file)

test_candidate_at_winning_counter:
  input  : c = 28738
  expect : equal to p above
\end{verbatim}

%---------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{references}

\end{document}
